Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-05-10 draft/accordionComplexSurfaces.tex
more details

% accordion and zigzag complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\ZC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{zz}}(#1)} % zigzag complex

@@

\title{Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide}

@@

\begin{abstract}
\end{abstract}

@@

@@

\vincent{Examples}

@@

\section{Accordion complex and zigzag complex}

@@

\subsection{Accordion complex and zigzag complex}

@@

@@

\section{All complexes coincide}

@@

\begin{proposition}
\label{prop:dualityKozul1}
For two dual dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q(\dissection)$ and~$\bar Q(\dissection\dual)$ are Kozul duals.
\end{proposition}

@@

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$. The construction also automatically defines two dual dissections~$\dissection(\bar Q)$ and~$\dissection\dual(\bar Q)$ of the surface~$\surface(\bar Q)$.
\end{definition}

\begin{proposition}
\label{prop:dualityKozul2}
For any gentle bound quiver~$\bar Q$ with Kozul dual~$\bar Q\dual$, the surfaces~$\surface(\bar Q)$ and~$\surface(\bar Q\dual)$ coincide, but~$\dissection(\bar Q\dual) = \dissection\dual(\bar Q)$ and~$\dissection\dual(\bar Q\dual) = \dissection(\bar Q)$.
\end{proposition}

@@

\begin{theorem}
\label{thm:complexesCoincide}
\begin{itemize}
\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the accordion complex~$\AC[\dissection(\bar Q)]$ and to the zigzag complex~$\ZC[\dissection\dual(\bar Q)]$.
\item For any pair of dual dissections~$\dissection, \dissection\dual$ of an oriented surface, the accordion complex~$\AC$ and the zigzag complex~$\ZC$ are isomorphic to the non-kissing complex~$\NKC[\bar Q(\dissection)]$.
\end{itemize}
\end{theorem}

>>>>

% accordion and zigzag complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\ZC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{zz}}(#1)} % zigzag complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex

@@

\title[Non-kissing and non-crossing complexes for gentle algebras]{Non-kissing and non-crossing complexes \\ for gentle algebras}

@@

\begin{abstract}
We consider three combinatorial models for the support $\tau$-tilting complex of a gentle bound quiver: the accordion complex, the zigzag complex, and the non-kissing complex. We unify these models in the same picture.
\end{abstract}

@@

Possible titles, depending on what we want to insist on:
\begin{enumerate}
\item Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide for gentle algebras
\item Non-kissing and non-crossing complexes for gentle algebras
\item Combinatorial models for support $\tau$-tilting on gentle algebras: accordion, zigzag and non-kissing complexes
\end{enumerate}

@@

\vincent{Examples}
\vincent{Should we introduce Koszul duality here and say what it does on quivers?}

@@

\section{Accordion complex, zigzag complex, and non-crossing complex}

@@

\subsection{Accordion complex, zigzag complex, and non-crossing complex}

@@

\begin{proof}
\vincent{Todo. I have the impression here that we need cellular embeddings.}
\end{proof}

\begin{definition}
\label{def:noncrossingComplex}
We call \defn{non-crossing complex} of the pair of dual dissections~$(\dissection, \dissection\dual)$ the simplicial complex~$\NCC = \AC = \ZC$.
\end{definition}

@@

\section{Non-kissing versus non-crossing}

In this section, we show that non-kissing complexes and non-crossing complexes actually coincide.
Namely, any pair of dual dissections~$(\dissection, \dissection\dual)$ defines a gentle bound quiver~$\bar Q_{\dissection, \dissection\dual}$ such that the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
Conversely, any gentle bound quiver~$\bar Q$ gives rise to a surface~$\surface_{\bar Q}$ equipped with a pair of dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ such that the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$.
In fact, we show that the accordion, zigzag, and non-kissing complexes can all be pictured in a unique way on the surface.
Interestingly, via the correspondence between pairs of dual dissections and gentle bound quivers, the duality between the dissections~$\dissection$ and~$\dissection\dual$ translates to the Koszul duality between the gentle algebras of~$\bar Q$ and~$\bar Q\dual$.

@@

\begin{proposition}
\label{prop:dualityKoszul1}
For two dual dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul duals.
\vincent{Here I mean that the gentle algebras are Koszul duals. We need to define that somewhere and discuss it on gentle quivers.}
\end{proposition}

@@

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$. The construction also automatically defines two dual dissections~$\dissection_{\bar Q}$ and~$\dissection\dual_{\bar Q}$ of the surface~$\surface_{\bar Q}$.
\end{definition}

\begin{proposition}
\label{prop:dualityKoszul2}
For any gentle bound quiver~$\bar Q$ with Koszul dual~$\bar Q\dual$, the surfaces~$\surface_{\bar Q}$ and~$\surface_{\bar Q\dual}$ coincide, but~$\dissection_{\bar Q\dual} = \dissection\dual_{\bar Q}$ and~$\dissection\dual_{\bar Q\dual} = \dissection_{\bar Q}$.
\end{proposition}

@@

\begin{theorem}
\label{thm:complexesCoincide}
\begin{itemize}
\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, \dissection\dual_{\bar Q}]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the zigzag complex~$\ZC[\dissection\dual_{\bar Q}]$.
\item For any pair of dual dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
\end{itemize}
\end{theorem}
